What factors can affect COVID-19 results?

### 2022-04-26 outputs/paper/paper.Rmd
final update I guess?

The paper mainly included four sections :\@ref(data), \@ref(model) , \@ref(results) and \@ref(discussion). \@ref(data) section covered the data cleaning process and removed the unused variables in this paper. We performed some exploratory data analysis (EDA) for the variables with the cleaned dataset. In the \@ref(model) section, we conducted a binomial regression model since we considered the results of the COVID-19 cases linearly correlated to the analyzed variables. We applied COVID-19 results as the response variables (either resolved or fatal), other variables were explanatory variables in the models. Then we ended up with the findings in the \@ref(results) section. Lastly, we discussed the bias and weakness of the dataset in the \@ref(discussion) section.

@@

Figures 3-7 demonstrate the distribution of COVID-19 cases outcome grouped by outbreak-associated, gender, age, infection, and classification, respectively. The results investigate the factors that may influence the  outcome. We noticed that most of the fatal/ resolved cases are sporadic (more than 30,000) instead of the outbreak associated in figure 3. Figure 4 shows there seems no significant difference between the number of females and males in fatal and resolved cases. But we need to consider further investigation. We observed that most of the resolved cases occurred between  19- younger and 50-59 years, similar to the fatal cases. Figure 6 indicates the ways of infection in resolved and fatal cases. We found community as one of the infection sources that most significantly affects the outcome.  Figure 7 displays the distribution of COVID-19 by classification. Most of the resolved cases are confirmed when all the fatal cases are confirmed. Moreover, the distribution of the COVID-19 outcome by every hospitalized, ever in ICU, ever intubated, respectively are shown in Section \@ref(appendix).

>>>>

The paper mainly included four sections : data \@ref(data), model \@ref(model) , result \@ref(results) and discussion\@ref(discussion). Data section \@ref(data) covered the data cleaning process and removed the unused variables in this paper. We performed some exploratory data analysis (EDA) for the variables with the cleaned dataset. In the model section \@ref(model), we conducted a binomial regression model since we considered the results of the COVID-19 cases linearly correlated to the analyzed variables. We applied COVID-19 results as the response variables (either resolved or fatal), other variables were explanatory variables in the models. Then we ended up with the findings in the result section \@ref(results). Lastly, we discussed the bias and weakness of the dataset in the discussion section \@ref(discussion).

@@

Figures 3-7 demonstrate the distribution of COVID-19 cases outcome grouped by outbreak-associated, gender, age, infection, and classification, respectively. The results investigate the factors that may influence the  outcome. We noticed that most of the fatal/ resolved cases are sporadic (more than 30,000) instead of the outbreak associated in figure 3. Figure 4 shows there seems no significant difference between the number of females and males in fatal and resolved cases. But we need to consider further investigation. We observed that most of the resolved cases occurred between  19- younger and 50-59 years, similar to the fatal cases. Figure 6 indicates the ways of infection in resolved and fatal cases. We found community as one of the infection sources that most significantly affects the outcome.  Figure 7 displays the distribution of COVID-19 by classification. Most of the resolved cases are confirmed when all the fatal cases are confirmed. Moreover, the distribution of the COVID-19 outcome by every hospitalized, ever in ICU, ever intubated, respectively are shown in section appendix \@ref(appendix).
